---
title             : "How playful are parents with their infants?"
shorttitle        : "Parental Playfulness Scale"

author: 
  - name          : "Marisol Basilio"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "mb773@cam.ac.uk"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ciara Laverty"
    affiliation   : "2"
    role:
      - Writing - Review & Editing

  - name          : "Claire Hughes"
    affiliation   : "3"
    role:
      - Writing - Review & Editing
affiliation:
  - id            : "1"
    institution   : "PEDAL, University of Cambridge"
  - id            : "2"
    institution   : "The LEGO Foundation"
  - id            : "3"
    institution   : "Centre for Family Research, University of Cambridge"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
knit              : worcs::cite_all
---

```{r setup, include = FALSE}
library("papaja")
library("worcs")
library(readxl)
library(here)
library(dplyr)
library(kableExtra)
library(magrittr)
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
# load_data()
r_refs("r-references.bib")
options(tinytex.verbose = TRUE)
```

```{r, echo=FALSE, message=FALSE}
library(Statamarkdown)
stataexe <- find_stata()
```


This manuscript uses the Workflow for Open Reproducible Code in Science [WORCS version 0.1.8, @vanlissaWORCSWorkflowOpen2020] to ensure reproducibility and transparency. All code <!--and data--> are available at <https://github.com/marisolbasilio/pps.git>.

This is an example of a non-essential citation [@vanlissaWORCSWorkflowOpen2020]. If you change the rendering function to `worcs::cite_essential`, it will be removed.

<!--The function below inserts a notification if the manuscript is knit using synthetic data. Make sure to insert it after load_data().-->
`r notify_synthetic()`

```{r, echo=FALSE, message=FALSE}
# Seed for random number generation
#set.seed(42)
#knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

```{stata, echo=FALSE, cleanlog=FALSE, results="hide"}
clear
clear mata
clear matrix
set more off
version 16.0
set maxvar 7000
*working directory:
cd "/Users/mb773/Documents/MBS Work/PPS/Paper 1/"
do "prog/1 Descriptives.do"
do "prog/1 RQ.do"
```

## Descriptives
```{r, echo=FALSE, message=FALSE}
# Add path of file 
xl_tables <- "/Users/mb773/Documents/MBS Work/PPS/Paper 1/output/tables.xlsx"

# Before reading data, we will return the names of the sheets for later use:
# excel_sheets(path = xl_tables)
# "desc"      "corr"      "retest"    "spearman"  "spearman2"

# Creating R data frames with each sheet
df_desc <- read_excel(path = xl_tables, sheet = "desc")
df_corr <- read_excel(path = xl_tables, sheet = "corr")
df_retest <- read_excel(path = xl_tables, sheet = "retest")
df_spearman <- read_excel(path = xl_tables, sheet = "spearman")
df_spearman2 <- read_excel(path = xl_tables, sheet = "spearman2")

# Creating tables
df_desc %>%
  kbl(caption = "Table 1. Descriptive Statistics", digits = 2) %>%
  kable_classic(full_width = F, html_font = "Times")
```

```{r, echo=FALSE, message=FALSE}
# Creating tables
df_corr %>%
  kbl(caption = "Table 2. Correlations", digits = 2) %>%
  kable_classic(full_width = T, html_font = "Times")
```



```{r, echo=FALSE, message=FALSE}
# Creating tables
df_retest %>%
  kbl(caption = "Table 3. Test-Retest", digits = 2) %>%
  kable_classic(full_width = F, html_font = "Times")
```



```{r, echo=FALSE, message=FALSE}
# Creating tables
df_spearman2 %>%
  kbl(caption = "Table 4. Spearman correlations", digits = 2) %>%
  kable_classic(full_width = F, html_font = "Times")
```



## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
